---
title: "Incident Trending"
author: "Tyler Virkler"
date: "February 5, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Installing Packages Needed
```{r, message=F, warning=F}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
library(tm)             # For vcorpus
library(tidyverse)      # data manipulation & plotting
library(stringr)        # text cleaning and regular expressions
library(tidytext)       # provides additional text mining functions
library(ggplot2)

devtools::install_github("dgrtwo/drlib") #To Install GitHub R Package for Plotting

```

#Reading Incident Dataset
```{r}
Idata <- read.csv(file = "Incidents_FEB17toFEB18.csv", header=TRUE)

```

#Writing Incident Description Column to .txt file for analysis
##By month
```{r}
write.table(Idata$Incident.Description,"IncidentDescription.txt",row.names=FALSE)

#Separate Text Captured by Month
Idata$month <- format(as.Date(Idata$Incident.Date, "%m/%d/%y"),"%m") #Create Month Column
Idata$month<- as.numeric(Idata$month)
Jan<-subset(Idata, month==01)
Feb<-subset(Idata, month==02)
Mar<-subset(Idata, month==03)
Apr<-subset(Idata, month==04)
May<-subset(Idata, month==05)
Jun<-subset(Idata, month==06)
Jul<-subset(Idata, month==07)
Aug<-subset(Idata, month==08)
Sep<-subset(Idata, month==09)
Oct<-subset(Idata, month==10)
Nov<-subset(Idata, month==11)
Dec<-subset(Idata, month==12)
#Write Text File to Combine all text for each month
write.table(Jan$Incident.Description,"001_IncidentDescription.txt",row.names=FALSE)
write.table(Feb$Incident.Description,"002_IncidentDescription.txt",row.names=FALSE)
write.table(Mar$Incident.Description,"003_IncidentDescription.txt",row.names=FALSE)
write.table(Apr$Incident.Description,"004_IncidentDescription.txt",row.names=FALSE)
write.table(May$Incident.Description,"005_IncidentDescription.txt",row.names=FALSE)
write.table(Jun$Incident.Description,"006_IncidentDescription.txt",row.names=FALSE)
write.table(Jul$Incident.Description,"007_IncidentDescription.txt",row.names=FALSE)
write.table(Aug$Incident.Description,"008_IncidentDescription.txt",row.names=FALSE)
write.table(Sep$Incident.Description,"009_IncidentDescription.txt",row.names=FALSE)
write.table(Oct$Incident.Description,"010_IncidentDescription.txt",row.names=FALSE)
write.table(Nov$Incident.Description,"011_IncidentDescription.txt",row.names=FALSE)
write.table(Dec$Incident.Description,"012_IncidentDescription.txt",row.names=FALSE)

```

#Loading File Location Folder Directory
```{r}
cname <- file.path("C:", "Users", "virklert", "Desktop", "IncidentTrending")
dir(cname)

```

#Gathering info on files located in the specified folder above.
```{r}
docs <- VCorpus(DirSource(cname))
summary(docs)
```

#Gathering Metadata on Txt file to analyze
```{r}
inspect(docs[1:12])
```

#Convert Txt files to character vector
```{r}
one <- unlist(docs[1], use.names=FALSE)
two <- unlist(docs[2], use.names=FALSE)
three <- unlist(docs[3], use.names=FALSE)

titles <- c("1", "2", "3")

books <- list(one, two, three)

series <- tibble()

for(i in seq_along(titles)) {
        
        clean <- tibble(chapter = seq_along(books[[i]]),
                        text = books[[i]]) %>%
             unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
             mutate(book = titles[i]) %>%
             select(book, everything())

        series <- rbind(series, clean)
}
```


# Set factor to keep books in order of publication
## Creating Bi-grams, or two word phrases
```{r}
series$book <- factor(series$book, levels = rev(titles))

series

```

#Frequency Analysis of bi-grams
```{r}
series %>%
        count(bigram, sort = TRUE)
```

#Remove Stop Words, or unimportant words
```{r}
series %>%
        separate(bigram, c("word1", "word2"), sep = " ") %>%
        filter(!word1 %in% stop_words$word,
               !word2 %in% stop_words$word) %>%
        count(word1, word2, sort = TRUE)
```

#Top Bi-grams for each month, or book
```{r}
series %>%
        separate(bigram, c("word1", "word2"), sep = " ") %>%
        filter(!word1 %in% stop_words$word,
               !word2 %in% stop_words$word) %>%
        count(book, word1, word2, sort = TRUE) %>%
        unite("bigram", c(word1, word2), sep = " ") %>%
        group_by(book) %>%
        top_n(10) %>%
        ungroup() %>%
        mutate(book = factor(book) %>% forcats::fct_rev()) %>%
        ggplot(aes(drlib::reorder_within(bigram, n, book), n, fill = book)) +
        geom_bar(stat = "identity", alpha = .8, show.legend = FALSE) +
        drlib::scale_x_reordered() +
        facet_wrap(~ book, ncol = 2, scales = "free") +
        coord_flip()
```

#Sentiment Analysis

```{r}
series %>%
        separate(bigram, c("word1", "word2"), sep = " ") %>%
        filter(word1 == "not") %>%
        count(book, word1, word2, sort = TRUE)

```

```{r}
AFINN <- get_sentiments("afinn")

(nots <- series %>%
        separate(bigram, c("word1", "word2"), sep = " ") %>%
        filter(word1 == "not") %>%
        inner_join(AFINN, by = c(word2 = "word")) %>%
        count(word2, score, sort = TRUE) 
)
```


```{r}
nots %>%
        mutate(contribution = n * score) %>%
        arrange(desc(abs(contribution))) %>%
        head(20) %>%
        ggplot(aes(reorder(word2, contribution), n * score, fill = n * score > 0)) +
        geom_bar(stat = "identity", show.legend = FALSE) +
        xlab("Words preceded by 'not'") +
        ylab("Sentiment score * # of occurrances") +
        coord_flip()
```



Visualizing N-gram netowrks, or what phrases are highly related.
```{r}
library(igraph)

(bigram_graph <- series %>%
        separate(bigram, c("word1", "word2"), sep = " ") %>%
        filter(!word1 %in% stop_words$word,
               !word2 %in% stop_words$word) %>%
        count(word1, word2, sort = TRUE) %>%
        unite("bigram", c(word1, word2), sep = " ") %>%
        filter(n > 20) %>%
        graph_from_data_frame()
)

```

#Plot Results
```{r}
library(ggraph)
set.seed(123)

a <- grid::arrow(type = "closed", length = unit(.15, "inches"))

ggraph(bigram_graph, layout = "fr") +
        geom_edge_link() +
        geom_node_point(color = "lightblue", size = 5) +
        geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
        theme_void()
```






